I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-27 lipics-master/experiments.tex
typo editing

The last network $6 \times 500$ (verification-agnostic) is the largest one. 
Results for CMP are good, at $65\%$ of verified images, comparable with $8\times 100$, taking less than $0.3s$ per neuron to perform the verification in average per image (there are more neurons, so longer runtime was expected). For comparison, results for $6 \times 500$ were not reported in \cite{crown,prima}. On this larger network, it is unclear whether the refined strategy of PRIMA and of $(\alpha)\beta$-CROWN is applicable, as the number of binary variables to encode even the first few layers is very large. As a matter of fact, refinedBaB is "NotImplemented" in $\alpha,\beta$-CROWN for this network, and the results are surprisingly inaccurate and fast in refinedPRIMA (even faster than for $5 \times 100$), probably because few/no nodes are actually refined. We thus resort and reported the standard pureBaB setting of $\alpha,\beta$-CROWN, with the usual 30s associated timeout. Accuracy on $\alpha,\beta$-CROWN is very low, only $15\%$ more images verified than DeepPoly. 
We also provided $\alpha,\beta$-CROWN with similar average time as CMP, setting the time-out at 2000s, giving $954s$ in average runtime ($925s$ for CMP). This only improved the accuracy 
of $\alpha,\beta$-CROWN by $3.5\%$, at $44.5\%$, with a runtime $50$ times longer. We conclude that the number of branches is often too high for $\alpha,\beta$-CROWN to tackle such a hard DNN. We also experimented MN-BaB \cite{ferrari2022complete} on $6 \times 500$. Results were similar to $\alpha,\beta$-CROWN: $40\%$ (18s) [30s Time-out] and $43\%$ (1036s) [2000s Time-out]; within 1.5\% of $\alpha,\beta$-CROWN.
For comparison, CMP could verify more than $20\%$ more images than $\alpha,\beta$-CROWN (or MN-BaB) with similar runtime (around 17min per image).

>>>>

The last network $6 \times 500$ (verification-agnostic) is the largest one. 
Results for CMP are good, at $65\%$ of verified images, comparable with $8\times 100$, taking less than $0.3s$ per neuron to perform the verification in average per image (there are more neurons, so longer runtime was expected). For comparison, results for $6 \times 500$ were not reported in \cite{crown,prima}. On this larger network, it is unclear whether the refined strategy of PRIMA and of $(\alpha)\beta$-CROWN is applicable, as the number of binary variables to encode even the first few layers is very large. As a matter of fact, refinedBaB is "NotImplemented" in $\alpha,\beta$-CROWN for this network, and the results are surprisingly inaccurate and fast in refinedPRIMA (even faster than for $5 \times 100$), probably because few/no nodes are actually refined. We thus resort and reported the standard pureBaB setting of $\alpha,\beta$-CROWN, with the usual 30s timeout. Accuracy on $\alpha,\beta$-CROWN is very low, only $15\%$ more images verified than DeepPoly. 
We also tested $\alpha,\beta$-CROWN with longer time-out, to understand $\alpha,\beta$-CROWN scaling. With time-out=$2000s$, the runtime of $\alpha,\beta$-CROWN is $954s$, comparable with $925s$ for CMP. This only improved the accuracy of $\alpha,\beta$-CROWN by $3.5\%$, at $44.5\%$, with a runtime $50$ times longer. We conclude that the number of branches is often too high for $\alpha,\beta$-CROWN to tackle such a hard verification-agnostic DNN. We also experimented MN-BaB \cite{ferrari2022complete} on $6 \times 500$. Results were similar to $\alpha,\beta$-CROWN: $40\%$ (18s) [30s Time-out] and $43\%$ (1036s) [2000s Time-out]; within 1.5\% of $\alpha,\beta$-CROWN. For comparison, CMP could verify more than $20\%$ more images than $\alpha,\beta$-CROWN (or MN-BaB) with similar runtime (around 17min per image).
